%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.5.1
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage[utf8]{inputenc}

\usepackage[scale=0.75]{geometry} % Reduce document margins

\newenvironment{verse}
\renewcommand{\poemtitlefont}{\normalfont\large\itshape\centering}
\usepackage{verse}
\usepackage{ifthen}

\newcommand{\attrib}[1]{%
\nopagebreak{\raggedleft\footnotesize #1\par}}

\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
% \setlength{\makecvheadnamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Almog} % Your first name
\familyname{Kurtser} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitae}
\mobile{(+972) 52 3630950}
\email{akurtser@gmail.com}
%\homepage{staff.org.edu/~jsmith}{staff.org.edu/$\sim$jsmith} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{additional information}
%\photo[60pt][4pt]{photos/almog} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"I actually think that I'm a rather optimistic and happy person; it's just that I'm not a very positive person, if you see the difference." - Linus Trovalds\newline{}}

%----------------------------------------------------------------------------------------
\ifxetex
  \usepackage{catchfile}
  \newcommand\getenv[2][]{%
    \immediate\write18{kpsewhich --var-value #2 > \jobname.tmp}%
    \CatchFileDef{\temp}{\jobname.tmp}{\endlinechar=-1}%
    \ifx\temp\empty\def\temp{UNDEFINED}\fi
    \if\relax\detokenize{#1}\relax\temp\else\let#1\temp\fi}
\else
    \usepackage{catchfile}
    \newcommand{\getenv}[2][]{%
      \CatchFileEdef{\temp}{"|kpsewhich --var-value #2"}{\endlinechar=-1}%
      \ifx\temp\empty\def\temp{UNDEFINED}\fi
      \if\relax\detokenize{#1}\relax\temp\else\let#1\temp\fi}
\fi

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage
%
%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents
%
%\makelettertitle % Print letter title
%
%\lipsum[4] % Dummy text
%
%\makeletterclosing % Print letter signature
%
%\newpage
\nopagenumbers % conditional rendering messes up with lastpage

\begin{document}

\getenv[\PRINTINTRODUCTION]{PRINTINTRODUCTION}

\ifthenelse{\equal{\PRINTINTRODUCTION}{true}}{
  \poemtitle{Introduction}

  \settowidth{\versewidth}{and enclose a Curriculum Vitae.}
  \begin{verse}[\versewidth]
  What must you do? \\
  You must submit an application \\
  and enclose a Curriculum Vitae.

  Regardless of how long your life is, \\
  the Curriculum Vitae should be short.

  Be concise, select facts. \\
  Change landscapes into addresses \\
  and vague memories into fixed dates.

  Of all your loves, mention only the marital, \\
  and of the children, only those who were born.

  It's more important who knows you \\
  than whom you know. \\
  Travels -- only if abroad. \\
  Affiliations -- to what, not why. \\
  Awards -- but not for what.

  Write as if you never talked with yourself, \\
  as if you looked at yourself from afar.

  Omit dogs, cats, and birds, \\
  mementos, friends, dreams.

  State price rather than value, \\
  title rather than content. \\
  Shoe size, not where one is going, \\
  the one you are supposed to be.

  Enclose a photo with one ear showing. \\
  What counts is its shape, not what it hears.

  What does it hear? \\
  The clatter of machinery that shreds paper.
  \end{verse}
  \attrib{Writing Curriculum Vitae / Włslawa Szymborska (1923--2012)}
}

\newpage
%----------------------------------------------------------------------------------------
%	CURRICULUM VITAE
%----------------------------------------------------------------------------------------

\makecvtitle % Print the CV title

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------


\section{Recent deeds/follies following Klarna TLV shutdown}
\cventry{05/2018--10/2019}{Thru-hiker}{\textsc{Pacific Crest Trail, INT, HRP}}{}{}{
Hiking 2,653 miles (4,270 km) from the U.S.--Mexico Border into Canada in an unbroken-continuous-footpath.\\
This hike took me through the states of California, Oregon, and Washington. \\
By the end, I've climbed well over 489,418 feet in elevation through 25 National Forests and 7 National Parks. \\
\newline
Shortly after that, I hiked the 683 mile long (1,100 km) Israel's National Trail.
Last but not least I took on a semi-winter conditions traverse of the 500+ mile long Haute Randonnée Pyrénéenne (HRP),
an unmarked high-route, stretching from the Atlantic to the Mediterranean.
To the best of my knowledge, I've being the last person to have successfully started (and completed it) for the 2019 hiking season in an unbroken-continuous-footpath despite abrupt winter conditions.
}

\section{Professional experience}
\cventry{11/2011--04/2018}{Software Developer}{\textsc{Klarna}}{Tel Aviv}{}{
  Developed, delivered, operated and maintained high quality software, used by millions of consumers and every merchant using Klarna:
\begin{itemize}
  \item Built a (near) real-time distributed data-enrichment service that matches partial textual transaction to categories and product images,
    processing ~1M data enrichment requests per day while handling wildly varying throughput with minimal latency. \\
    Enabled by \textsc{Kafka} + \textsc{Node.js}, \textsc{Jenkins} CI/CD pipeline, monitoring with \textsc{Grafana} + \textsc{Prometheus}, deployed with \textsc{Docker} on AWS.
  \item Developed Klarna's largest consumer facing system - started as classic RoR and evolved into a \textsc{React} Single Page App + \textsc{Rails} backed API, serving and aggregating content from dozens of microservices.
  \item Designed and developed Klarna's merchant facing order management system, improving the everyday lives of many thousands of merchants. \\
    Based on \textsc{Rails}, \textsc{AngularJS}, \textsc{Sinatra} (for API + OAuth 2) and \textsc{Solr} to enable searching up to 3 years of data.
  \item Took part in developing Klarna's first non-manual merchants onboarding system, allowing salesperson to focus on sales rather than paperwork.
\end{itemize}}

\cventry{2007--2009}{Software Developer}{\textsc{Kaltura}}{Ramat Gan}{}{Joined as the 3rd developer,
built a video editing, management and streaming platform using Flex/Actionscript as well as \textsc{Python} for automation. }
\cventry{2006--2007}{Software Developer}{\textsc{Zone4Play}}{Tel Aviv}{}{Refactored an existing gaming system by migrating its front-end from http polling to work against a Java EE backend using TCP sockets, enabling code reuse and and making efficient use of network resources that resulted in 50\% decrease in overall backend resources usage which led to reduced operational cost.}
\cventry{2003--2006}{Criminal Investigator \& Computer Forensics Analyst}{The Central Unit for Special Investigations}{\textsc{IDF} (mandatory regular service)}{}{Leading and teaming on dozens of investigations ranging from frauds (few of which costed millions to the taxpayer), weapons theft, drug trade and violence.
}
%------------------------------------------------

%----------------------------------------------------------------------------------------
%	COMPUTER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{Recently used languages/technologies}

\cvitem{Control plane}{\textsc{Python}, \textsc{Ruby}, \textsc{(modern) JS/Node}, \textsc{Bash}, \LaTeX, \textsc{Docker}, \textsc{Jenkins}}
\cvitem{Data plane}{\textsc{Postgresql}, \textsc{Redis}, \textsc{Kafka}}

\section{Technologies I lack experience with but would love to use on my next job:}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Rust}{Haskell}
\cvlistdoubleitem{TLA+}{CRDTs}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{Areas of interest}

\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

\cvlistdoubleitem{Distributed systems}{Competitive programming}
\cvlistdoubleitem{Long distance hiking}{Trail running}
\cvlistdoubleitem{Fantasy \& Sci-Fi}{Woodworking}
\cvlistitem{Using sourdough to make friends and enemeies alike}
\cvlistitem{Seamstering (mostly under the pretext of manufacturing hiking gear)}

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	VOLUNTEERING SECTION
%----------------------------------------------------------------------------------------

\section{Volunteering}
\cventry{2014-2017}{Herzelia Loves Animals}{}{}{}{Rescuing, fostering and finding new homes for stray dogs}
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	LANGUAGES SECTION
%----------------------------------------------------------------------------------------

\section{Languages}

\cvitemwithcomment{English}{Native or bilingual proficiency}{}
\cvitemwithcomment{Hebrew}{Native or bilingual proficiency}{}


%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2009--2010}{ Earned partial credit toward a B.Sc in Computer Science and Mathematics}{The Open University of Israel}{}{}{}

\end{document}

%----------------------------------------------------------------------------------------
%	PRESENTATIONS SECTION
%----------------------------------------------------------------------------------------

\section{Talks}

\cventry{2017}{Git Under The Hood}{}{}{}{Live coding exploration of git's object model and operations using plumbing command.}

